Discriminative Sensing Based on Signal Processing for Information Security Analysis

### 2017-11-15 docs/thesis/chapters/1_introduction/introduction.tex
tensor-dl and spell check

\begin{enumerate}
	\item We propose an approach based on eigen similarity analysis for extracting detailed information about accurate time and network ports under network attack, and evaluated the accuracy and performance of the proposed framework applied to a experimental scenario and to the DARPA 1998 dataset;
	\item We discuss the computational complexity of the proposed framework and evaluate the required processing time for tested scenarios;
	\item We propose an architechture and techniques for offline behavioral analysis of a corporate mobile client security architecture;
	\item We discuss the processing time of the proposed framework for mobile devices;
	\item We propose a tensor-based dictionary learning approach for fraud detection in mobile payment transactions;
\end{enumerate}

>>>>

\begin{enumerate}
	\item We propose an approach based on eigen similarity analysis for extracting detailed information about accurate time and network ports under network attack, and evaluated the accuracy and performance of the proposed framework applied to an experimental scenario and to the DARPA 1998 dataset;
	\item We discuss the computational complexity of the proposed framework and evaluate the required processing time for tested scenarios;
	\item We propose an architechture and techniques for offline behavioral analysis of a corporate mobile client security architecture;
	\item We discuss the processing time of the proposed framework for mobile devices;
	\item We propose a tensor-based dictionary learning approach for fraud detection in mobile payment transactions;
\end{enumerate}

### 2017-11-15 docs/thesis/chapters/2_eigen_similarity/eigen_similarity.tex
tensor-dl and spell check

In this work, scalars are denoted by italic letters ($a, b, A, B, \alpha, \beta$), vectors by lowercase bold letters (\textbf{a, b}), matrices by uppercase bold letters (\textbf{A, B}), and $a_i,_j$ denotes the (\emph{i, j}) elements of the matrix \textbf{A}. The superscripts \textsuperscript{T} and \textsuperscript{-1} are used for matrix transposition and matrix inversion, respectively. We define the operator $\rm diag(\cdot)$ that returns the vector of the main diagonal of a given matrix, the operator $\rightarrow$, which denotes the deletion of a given element from a set and the operator $\#$, that returns the rank of a matriz, and the operator $\sim$ that sorts the elements of a vector in ascending order.

@@

\begin{equation}\label{eq:eq01}
\boldsymbol{X}^{(q)} = \boldsymbol{U}^{(q)} + \boldsymbol{N}^{(q)} + \boldsymbol{A}^{(q)},
\end{equation}
where $q$ represents the $q$-th time frame, which is a time grouping of network traffic. The matrix $\boldsymbol{X}^{(q)} \in \mathbb{R}^{M \times N}$ consists of \emph{M} rows and \emph{N} columns. Each row represents a communication port (TCP port or UDP port), and each column represents time bins having a approtiate size, such as one minute. Each element $x_{m,n}^{(q)}$ stands for the number of times that the port $m$ appears at the $n$-th minute, at the $q$-th time frame.

@@

In TCP SYN scan, a SYN packet is sent to the destination and two types of responses may occur: SYN/ACK or RST/ACK. In the first case, the destination port is in the listening state, in the second case, the destination port is not listening. At the end of each port scanning, a RST/ACK packet is sent by the system that is performing the port scan. Therefore, a full connection or a complete three-way handshake is never established, which makes the detection of the attack sender more difficult, and requires approaches able to identify probe attacks without connection stablishment. The UDP scan technique sends UDP packets to the destination port, and if it responds with a \emph{ICMP port unreachable} message, then it indicates that the scanned port is closed. On the other hand, if a message is not received, then the port is considered as open.

@@

This section describes the proposed technique to detect synflood, fraggle and port scan, according to Figure \ref{fig:2_fig80}, which represents the overview of the proposed framework for detection and identification of network attacks. In Subsection \ref{sec:2_prop_LargestEigenvaluebyTimeFrames} we present the steps for extraction of the largest eigenvelue for each $q$-th time frame. Next, in Subsection \ref{sec:2_prop_MOSSchemes}, we show how to apply the eiganvalues on the MOS scheme in order to detect the attack. In Subsection \ref{sec:2_prop_EigenvalueAnalysis}, we present the eigenvalue analysis to identify the time frames detected as under attack, and the Subsection \ref{sec:2_prop_EigenSimilarityAnalysis} describes the similarity analysis evaluated for detailed attack identification.

@@

After the estimation of the $\rm{\boldsymbol{\hat{q}}}_{\rm max}$ time frames under attack, it is necessary to obtain more details of the detected Attacks, such as the $n$-th minutes when the attacks happened and the $m$-th network ports that were attacked. To deal with this problem, the adoption of a similarity analysis between legitimate traffic and the traffic of time frames estimated as under attack is evaluated, analysing the effectiveness of cosine similarity to highlight abnormalies inserted by network traffic attacks.

@@

For eigen similarity analyis, we evaluate the cosine similarity in order to identify lacks of similarity between legitimate and malicious traffic, as follows

@@

The most significant eigenvector $\boldsymbol{v}^{(q)}$, of a time frame $q$ without attack, can be derivated from (\ref{eq:eq06}) and selected according to the eigenvector of the largest eigenvalue $\lambda_1^{(q)}$, which is the principal component of the evaluated matrix. The same calculation shall be performed in order to obtain the target eigenvectors $\boldsymbol{v}_{(n)}$, calculated from a time frame without attack plus minutes of a time frame estimated as under attack, to evaluate the occurrence of network attacks.

The reference eigenvectors $\boldsymbol{v}^{(q)}$ is calculated from the traffic whithout attack, from a time frame $q$ composed of $Q$ minutes of legitimate network traffic. For the detailed attack identification, each $\boldsymbol{x}^{(\hat{q})}_{(n)}$ vector of each $n$-th minutes of the estimated $\rm{\boldsymbol{\hat{q}}}_{\rm max}$ time frames shall be individually appended into $\boldsymbol{X}^{(q)}$, as represented by

@@

Figure \ref{fig:2_fig8} ilustrates the network traffic selection for the incremental approach of eigen similarity analysis, where the $\boldsymbol{X}^{(1)}$ is chosen as reference for similarity analysis of the $m$-th minutes of the time frame $q=3$, where one network attack was previously detected.

@@

The eigen similarity analysis starts at $\boldsymbol{x}^{(3)}_{(41)}$ and is incrementally performed until $\boldsymbol{x}^{(\hat{3})}_{(60)}$, in order to calculate the $s_n$. We assume that $s_n < l$ means an attack identification, according the anomaly on similiarity of $s_n$ to a defined limiar $l$. Therefore, after obtaining the most significant eigenvector $\boldsymbol{v}^{(q)}$ and the target eigenvectors $\boldsymbol{v}_{(n)}$ for eigen similarity analyis, the $s_n$ is calculated according to~(\ref{eq:eq11}).

@@

For similarity analyis, each $m$-th port of the last $n$-th minute of $\boldsymbol{X}_n$, denoted as $x_{(m,n)}$, shall be individually replaced by the traffic of the evaluated $m$-th port of the $\hat{n}$-th minute under attack, denoted as $x^{(\hat{q})}_{(m,\hat{n})}$, in order to identify significant variation on similarity caused by the traffic of the $m$-th port.

@@

In Table \ref{tab:tab4}, two MOS schemes outperforms from the others, EDC and EFT. Efficient Detection Criterion (EDC) and Exponential Fitting Test (EFT) are the most effective schemes, correctly estimating the number of attacks in comparison to the expected values for effetctive attack detection, as defined by the column of real values in Table \ref{tab:tab4}. The AIC and MDL schemes are satisfactory only for port scan detection, however SURE and RADOI schemes did not show effective results for port scan or flood detection.

@@

According to Table \ref{tab:tab4}, EDC and EFT estimated correctly the number of attacks of a time frame vector, indicating that ocurred $\hat{d}$ network attacks, but not providing additional details, what highlights the necessity of complementary approaches in order to estimate the time and ports under attack. Hence, we propose apply eigen analysis to estimate the $q$-th time frames under attack and eigen similarity analysis to estimate the minutes and ports under attack.

@@

Therefore, we conclude that the $\hat{d}$ largest eigenvalues correspond to the respectives $q$-th time frames under attack, which is denoted by $\rm{\boldsymbol{\hat{q}}}_{\rm max}$ and can be calculated according to Algorithm \ref{alg:2_alg01}.

@@

Comparing the approaches for similarity analysis, it is possible to observe that all approaches highlight the low similarity when evaluated the traffic under attack. However, the incremental approach figured out low similarity for times without attack, where $n=16, 17, 18, 19, 20$, what indicates that the incremental approach can produce false posive results. This behavior occurs because the incremental approaches appends all selected traffic into the reference traffic for comparison against the original reference traffic, what makes more evident the first lack of similarity but reduces the changing detection capability after an attack detection.

@@

Comparing the incremental individualized and the individual approaches for eigen similarity analysis, it is possible to observe that the incremental individualized approach obtain lowest values for almost all cases, except for the time $n=14$, where incremental individualized approach identified a larger similarity than the individual approach. The incremental individualized appends information about each evaluated traffic, therefore it incorporates traffic behaviors that can reduce the outlier capability detection, as ocurred for the time $n=14$.

@@

For fraggle attack detection, the lack of similarity between legitimate and malicious traffic was more evident than for the evaluation of synflood and port scan detecion. This behavior can be explained by the number of packets generated through the fraggle attack simulation, that was significative larger than the number of packets generated during the synflood simulation. Considering the three approaches, the largest value for times under attack was 0.0083, while the shortest value for times without attacks was 0.9993.

@@

The incremental individualized approach presented more sensibility to anomaly detection than the individual approach, the former produced the identification of a low similarity of 0.0298 for almost all ports under attack, unless the port 21, although the simulation has attacked this port. The individual approach was not able to identify low similarity for ports under attack, resunting in values of 0.9997 for ports with anomalous traffic and 0.9999 for ports without network attack.

For the evaluation of the proposed approaches for identification of ports under synflood and fraggle attack, all minutes of each time frame, in which one attack location was estimated, were analyzed. Even though, due to space limitations, only the results of the firt minute where a low similarity was idenfified will be shown such as where $n=11$. Nevertheless, the results obtained for the evaluation of traffic without attack presented high similarity to the reference traffic, with similarities close to 0.9999, and the evaluation of the other minutes under attack presented results quite similar to the resuts shown in the Tables \ref{tab:tab9} and \ref{tab:tab10}.

@@

According to results presented in Table \ref{tab:tab9}, both approches identifies low similarity for the traffic of port 600, which is the target port of the simulated synflood attack, but the incremental individualized approach identifies the lowest similarity and presents better sensibility to identification of synflood attack through eigen similarity analysis assisted by threshold definition.

@@

The results for the avaluation of ports under fraggle attack, shown in Table \ref{tab:tab10}, were similar to the results obtained for synflood analysis, with the identification of low similarity for traffic of the port under attack. Nevertheless, for fraggle analysis, the individual approach identified the lowest similarity, that is 0.0004 while the incremental individualized approach obtained a similarity of 0.0031.

@@

Since the proposed framework focus on flood and probe attack detection, only the attacks with behavior similar to flood or probe attack were evaluated. Initially all DoS and probe attacks were selected, but it was observed that the most cases of DoS focus on exploit system vulnerabilities instead of flooding attack, and most of probe attacks focus on ICMP intead of port scanning. Therefore, for evaluation of the proposed approach for flood and probe attack detection, it is necessary to select cases that implements flood or port scan behaviors. The following week-day-attack cases  were selected:

@@

Therefore, the proposed framework is $O(N^3 + Q \log Q + \hat{d}Q + N^3)$ and its worst-case running time is $O(N^3)$. The computational complexity of EVD is predominant in the framework, but the approach splits the data into time frames with period time $N$, which makes possible to limitate the growth of $N$ even for evaluations of cases with total time larger than $N$, reducing the impact caused by the computational complexity of EVD.

@@

Future research is directed to improvements for obtaining better false positive rates, as well as for make the proposed framework able to identify sparse probe attacks or subtle behaviors, such as exfiltration or covert communication, considering the evaluation of a flow-based analysis and novel datasets. Distributed or parallel processing can also be evaluated to analyze the scalability and processing capacity for monitoring high thoughput network traffic. Additionally, future research can evaluate the application of the proposed approach to different attack types and domains, considering cases that are aware to behavioral analysis.

>>>>

In this work, scalars are denoted by italic letters ($a, b, A, B, \alpha, \beta$), vectors by lowercase bold letters (\textbf{a, b}), matrices by uppercase bold letters (\textbf{A, B}), and $a_i,_j$ denotes the (\emph{i, j}) elements of the matrix \textbf{A}. The superscripts \textsuperscript{T} and \textsuperscript{-1} are used for matrix transposition and matrix inversion, respectively. We define the operator $\rm diag(\cdot)$ that returns the vector of the main diagonal of a given matrix, the operator $\rightarrow$, which denotes the deletion of a given element from a set and the operator $\#$, that returns the rank of a matrix, and the operator $\sim$ that sorts the elements of a vector in ascending order.

@@

\begin{equation}\label{eq:eq01}
\boldsymbol{X}^{(q)} = \boldsymbol{U}^{(q)} + \boldsymbol{N}^{(q)} + \boldsymbol{A}^{(q)},
\end{equation}
where $q$ represents the $q$-th time frame, which is a time grouping of network traffic. The matrix $\boldsymbol{X}^{(q)} \in \mathbb{R}^{M \times N}$ consists of \emph{M} rows and \emph{N} columns. Each row represents a communication port (TCP port or UDP port), and each column represents time bins having a appropriate size, such as one minute. Each element $x_{m,n}^{(q)}$ stands for the number of times that the port $m$ appears at the $n$-th minute, at the $q$-th time frame.

@@

In TCP SYN scan, a SYN packet is sent to the destination and two types of responses may occur: SYN/ACK or RST/ACK. In the first case, the destination port is in the listening state, in the second case, the destination port is not listening. At the end of each port scanning, a RST/ACK packet is sent by the system that is performing the port scan. Therefore, a full connection or a complete three-way handshake is never established, which makes the detection of the attack sender more difficult, and requires approaches able to identify probe attacks without connection establishment. The UDP scan technique sends UDP packets to the destination port, and if it responds with a \emph{ICMP port unreachable} message, then it indicates that the scanned port is closed. On the other hand, if a message is not received, then the port is considered as open.

@@

This section describes the proposed technique to detect synflood, fraggle and port scan, according to Figure \ref{fig:2_fig80}, which represents the overview of the proposed framework for detection and identification of network attacks. In Subsection \ref{sec:2_prop_LargestEigenvaluebyTimeFrames} we present the steps for extraction of the largest eigenvalue for each $q$-th time frame. Next, in Subsection \ref{sec:2_prop_MOSSchemes}, we show how to apply the eigenvalues on the MOS scheme in order to detect the attack. In Subsection \ref{sec:2_prop_EigenvalueAnalysis}, we present the eigenvalue analysis to identify the time frames detected as under attack, and the Subsection \ref{sec:2_prop_EigenSimilarityAnalysis} describes the similarity analysis evaluated for detailed attack identification.

@@

After the estimation of the $\rm{\boldsymbol{\hat{q}}}_{\rm max}$ time frames under attack, it is necessary to obtain more details of the detected Attacks, such as the $n$-th minutes when the attacks happened and the $m$-th network ports that were attacked. To deal with this problem, the adoption of a similarity analysis between legitimate traffic and the traffic of time frames estimated as under attack is evaluated, analyzing the effectiveness of cosine similarity to highlight abnormalities inserted by network traffic attacks.

@@

For eigen similarity analysis, we evaluate the cosine similarity in order to identify lacks of similarity between legitimate and malicious traffic, as follows

@@

The most significant eigenvector $\boldsymbol{v}^{(q)}$, of a time frame $q$ without attack, can be derivate from (\ref{eq:eq06}) and selected according to the eigenvector of the largest eigenvalue $\lambda_1^{(q)}$, which is the principal component of the evaluated matrix. The same calculation shall be performed in order to obtain the target eigenvectors $\boldsymbol{v}_{(n)}$, calculated from a time frame without attack plus minutes of a time frame estimated as under attack, to evaluate the occurrence of network attacks.

The reference eigenvectors $\boldsymbol{v}^{(q)}$ is calculated from the traffic without attack, from a time frame $q$ composed of $Q$ minutes of legitimate network traffic. For the detailed attack identification, each $\boldsymbol{x}^{(\hat{q})}_{(n)}$ vector of each $n$-th minutes of the estimated $\rm{\boldsymbol{\hat{q}}}_{\rm max}$ time frames shall be individually appended into $\boldsymbol{X}^{(q)}$, as represented by

@@

Figure \ref{fig:2_fig8} illustrates the network traffic selection for the incremental approach of eigen similarity analysis, where the $\boldsymbol{X}^{(1)}$ is chosen as reference for similarity analysis of the $m$-th minutes of the time frame $q=3$, where one network attack was previously detected.

@@

The eigen similarity analysis starts at $\boldsymbol{x}^{(3)}_{(41)}$ and is incrementally performed until $\boldsymbol{x}^{(\hat{3})}_{(60)}$, in order to calculate the $s_n$. We assume that $s_n < l$ means an attack identification, according the anomaly on similarity of $s_n$ to a defined limiar $l$. Therefore, after obtaining the most significant eigenvector $\boldsymbol{v}^{(q)}$ and the target eigenvectors $\boldsymbol{v}_{(n)}$ for eigen similarity analysis, the $s_n$ is calculated according to~(\ref{eq:eq11}).

@@

For similarity analysis, each $m$-th port of the last $n$-th minute of $\boldsymbol{X}_n$, denoted as $x_{(m,n)}$, shall be individually replaced by the traffic of the evaluated $m$-th port of the $\hat{n}$-th minute under attack, denoted as $x^{(\hat{q})}_{(m,\hat{n})}$, in order to identify significant variation on similarity caused by the traffic of the $m$-th port.

@@

In Table \ref{tab:tab4}, two MOS schemes outperforms from the others, EDC and EFT. Efficient Detection Criterion (EDC) and Exponential Fitting Test (EFT) are the most effective schemes, correctly estimating the number of attacks in comparison to the expected values for effective attack detection, as defined by the column of real values in Table \ref{tab:tab4}. The AIC and MDL schemes are satisfactory only for port scan detection, however SURE and RADOI schemes did not show effective results for port scan or flood detection.

@@

According to Table \ref{tab:tab4}, EDC and EFT estimated correctly the number of attacks of a time frame vector, indicating that occurred $\hat{d}$ network attacks, but not providing additional details, what highlights the necessity of complementary approaches in order to estimate the time and ports under attack. Hence, we propose apply eigen analysis to estimate the $q$-th time frames under attack and eigen similarity analysis to estimate the minutes and ports under attack.

@@

Therefore, we conclude that the $\hat{d}$ largest eigenvalues correspond to the respective $q$-th time frames under attack, which is denoted by $\rm{\boldsymbol{\hat{q}}}_{\rm max}$ and can be calculated according to Algorithm \ref{alg:2_alg01}.

@@

Comparing the approaches for similarity analysis, it is possible to observe that all approaches highlight the low similarity when evaluated the traffic under attack. However, the incremental approach figured out low similarity for times without attack, where $n=16, 17, 18, 19, 20$, what indicates that the incremental approach can produce false positive results. This behavior occurs because the incremental approaches appends all selected traffic into the reference traffic for comparison against the original reference traffic, what makes more evident the first lack of similarity but reduces the changing detection capability after an attack detection.

@@

Comparing the incremental individualized and the individual approaches for eigen similarity analysis, it is possible to observe that the incremental individualized approach obtain lowest values for almost all cases, except for the time $n=14$, where incremental individualized approach identified a larger similarity than the individual approach. The incremental individualized appends information about each evaluated traffic, therefore it incorporates traffic behaviors that can reduce the outlier capability detection, as occurred for the time $n=14$.

@@

For fraggle attack detection, the lack of similarity between legitimate and malicious traffic was more evident than for the evaluation of synflood and port scan detection. This behavior can be explained by the number of packets generated through the fraggle attack simulation, that was significantly larger than the number of packets generated during the synflood simulation. Considering the three approaches, the largest value for times under attack was 0.0083, while the shortest value for times without attacks was 0.9993.

@@

The incremental individualized approach presented more sensibility to anomaly detection than the individual approach, the former produced the identification of a low similarity of 0.0298 for almost all ports under attack, unless the port 21, although the simulation has attacked this port. The individual approach was not able to identify low similarity for ports under attack, resulting in values of 0.9997 for ports with anomalous traffic and 0.9999 for ports without network attack.

For the evaluation of the proposed approaches for identification of ports under synflood and fraggle attack, all minutes of each time frame, in which one attack location was estimated, were analyzed. Even though, due to space limitations, only the results of the first minute where a low similarity was identified will be shown such as where $n=11$. Nevertheless, the results obtained for the evaluation of traffic without attack presented high similarity to the reference traffic, with similarities close to 0.9999, and the evaluation of the other minutes under attack presented results quite similar to the results shown in the Tables \ref{tab:tab9} and \ref{tab:tab10}.

@@

According to results presented in Table \ref{tab:tab9}, both approaches identifies low similarity for the traffic of port 600, which is the target port of the simulated synflood attack, but the incremental individualized approach identifies the lowest similarity and presents better sensibility to identification of synflood attack through eigen similarity analysis assisted by threshold definition.

@@

The results for the evaluation of ports under fraggle attack, shown in Table \ref{tab:tab10}, were similar to the results obtained for synflood analysis, with the identification of low similarity for traffic of the port under attack. Nevertheless, for fraggle analysis, the individual approach identified the lowest similarity, that is 0.0004 while the incremental individualized approach obtained a similarity of 0.0031.

@@

Since the proposed framework focus on flood and probe attack detection, only the attacks with behavior similar to flood or probe attack were evaluated. Initially all DoS and probe attacks were selected, but it was observed that the most cases of DoS focus on exploit system vulnerabilities instead of flooding attack, and most of probe attacks focus on ICMP instead of port scanning. Therefore, for evaluation of the proposed approach for flood and probe attack detection, it is necessary to select cases that implements flood or port scan behaviors. The following week-day-attack cases  were selected:

@@

Therefore, the proposed framework is $O(N^3 + Q \log Q + \hat{d}Q + N^3)$ and its worst-case running time is $O(N^3)$. The computational complexity of EVD is predominant in the framework, but the approach splits the data into time frames with period time $N$, which makes possible to limit the growth of $N$ even for evaluations of cases with total time larger than $N$, reducing the impact caused by the computational complexity of EVD.

@@

Future research is directed to improvements for obtaining better false positive rates, as well as for make the proposed framework able to identify sparse probe attacks or subtle behaviors, such as exfiltration or covert communication, considering the evaluation of a flow-based analysis and novel datasets. Distributed or parallel processing can also be evaluated to analyze the scalability and processing capacity for monitoring high throughput network traffic. Additionally, future research can evaluate the application of the proposed approach to different attack types and domains, considering cases that are aware to behavioral analysis.

### 2017-11-15 docs/thesis/chapters/3_mobile/mobile.tex
tensor-dl and spell check

This work proposes an archtecture and approach for user behavior analysis based on Model Order Selection (MOS) \cite{tenorio2013greatest}, in order to detect possible threats, and to reduce the risks and the harm of the most common threats, which are the expired user misusing password and the intruder attack. The key expiration period is safely incorporated into the proposed system solution in order to enhance security. Additionally, the behavioral analysis can indicate well known malicious behaviors, their variations, as well as novel attacks, which present low or high variance in comparison to legitimate user behaviors.

The work is structured as follows. Section \ref{sec:3_related_works} analyzes the most common security problems in the mobile cloud environment and the solutions for offline protection in the BYOD world. Section \ref{sec:3_the_client_security_architecture} outlines the mobile security architecture of the proposed solution. Section \ref{sec:3_offline_mode} presents the detailed scheme of the proposed solution to the problem of offline mobile client security. Section \ref{sec:3_mos} explains the algorithms for MOS. Section \ref{sec:3_results} discusses the common threat scenarios, the data modeling, the complexity analysis and dicussion of the practical implementation results. Section \ref{sec:3_conclusion} concludes the chapter.

@@

In many cases the industrial providers of the mobile security API avoid the problem by completely forbidding the offline access to the protected app, i.e. SAP Mocona, which operates as a secure client wrapping layer \cite{Lelyveld2013}. Due to various constraints such as traffic load, travelling and ease of access, the SME business procedure may require such access.

@@

Figure \ref{fig:3_02} depicts the client-side protection mechanisms. The client should support 4 subsystems: i) encryption subsystem (\textbf{Online/Offline Criptography}) that contains the procedures of encryption and decryption; ii) storage subsystem (\textbf{Protected Storage}) that provides the downloaded shares and key storage protection; iii) (\textbf{threat intelligence}) unit that provides the constant monitoring, and iv) the communication subsystem (\textbf{Communication with Server}). In short, all security procedures are connected to 4 groups of operations: file request and receiving; encryption and decryption; file and key storing; monitoring and analysis.

>>>>

This work proposes an architecture and approach for user behavior analysis based on Model Order Selection (MOS) \cite{tenorio2013greatest}, in order to detect possible threats, and to reduce the risks and the harm of the most common threats, which are the expired user misusing password and the intruder attack. The key expiration period is safely incorporated into the proposed system solution in order to enhance security. Additionally, the behavioral analysis can indicate well known malicious behaviors, their variations, as well as novel attacks, which present low or high variance in comparison to legitimate user behaviors.

The work is structured as follows. Section \ref{sec:3_related_works} analyzes the most common security problems in the mobile cloud environment and the solutions for offline protection in the BYOD world. Section \ref{sec:3_the_client_security_architecture} outlines the mobile security architecture of the proposed solution. Section \ref{sec:3_offline_mode} presents the detailed scheme of the proposed solution to the problem of offline mobile client security. Section \ref{sec:3_mos} explains the algorithms for MOS. Section \ref{sec:3_results} discusses the common threat scenarios, the data modeling, the complexity analysis and discussion of the practical implementation results. Section \ref{sec:3_conclusion} concludes the chapter.

@@

In many cases the industrial providers of the mobile security API avoid the problem by completely forbidding the offline access to the protected app, i.e. SAP Mocona, which operates as a secure client wrapping layer \cite{Lelyveld2013}. Due to various constraints such as traffic load, traveling and ease of access, the SME business procedure may require such access.

@@

Figure \ref{fig:3_02} depicts the client-side protection mechanisms. The client should support 4 subsystems: i) encryption subsystem (\textbf{Online/Offline Cryptography}) that contains the procedures of encryption and decryption; ii) storage subsystem (\textbf{Protected Storage}) that provides the downloaded shares and key storage protection; iii) (\textbf{threat intelligence}) unit that provides the constant monitoring, and iv) the communication subsystem (\textbf{Communication with Server}). In short, all security procedures are connected to 4 groups of operations: file request and receiving; encryption and decryption; file and key storing; monitoring and analysis.
